\tool: Revisiting BadUSB with Type-C

### 2021-01-25 WOOT/Files/related_work.tex
polish table

Under the premise of ensuring the full functionality of USB devices, there have been some works trying to improve the security during connection establishment.
Windows Defender ATP\cite{windenfenderwhite} maintains a whitelist of USB devices, only devices on the whitelist are allowed to communicate with the host. This prevents all potential attacks from untrusted devices. But this requires users to have a certain safety awareness and technical background to maintain a valid whitelist. For example, a naive user may add the USB device from unknown sources to his/her whitelist without precaution. There are designs can overcome this drawback. For instance, Mohammadmoradi et al\cite{mohammadmoradi2018making} proposes a strategy to generate such a whitelist automatically. This strategy first generates a unique fingerprint for each device based on its functionality. Then these fingerprints are used to maintain a safe and valid whitelist of USB devices. There is another work mediating USB connectivity for Industrial Control. TMSUI\cite{yang2015tmsui} relies on rich experience of administrators to build a whitelist. However, some modified USB devices may hide their real functionality from the user.

@@

We summarize the former effort in USB attack and defense in Table~\ref{table:attack_vs_defense}, which illustrates the effectiveness of each defense against various attacks including our \tool.
\newcommand{\circlefull}{\includegraphics[scale=0.025]{Figs/circle_full.png}}
\newcommand{\circlehalf}{\includegraphics[scale=0.025]{Figs/circle_half.png}}
\newcommand{\circleempty}{\includegraphics[scale=0.025]{Figs/circle_empty.png}}
\begin{table*}
	\centering
	\begin{tabular}{|c|c|c|c|c|c|c|c|c|}

		\hline
		\diagbox[width=1.46in] {Defence}{Attack} & Facedancer\cite{facedancer}, Syzkaller\cite{syzkaller} & \cite{rubber,badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver} & JFC\cite{JFC}&Duqu\cite{duqu}& \cite{brain, stuxnet, conficker,flame}&\cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} &\cite{usbkiller, cable, usbee, turnip}&Armory\\
		\hline 
		USB condom \cite{Condom}& \circlefull & \circlefull & \circlefull & \circlefull &\circlefull& \circlefull& \circlefull &\circlefull\\
		\hline 
		Windows Defender ATP\cite{windenfenderwhite}, Mohammadmoradi et al\cite{mohammadmoradi2018making}, TMSUI\cite{yang2015tmsui}& \circleempty & \circlehalf & \circlehalf & \circlehalf &\circlehalf& \circleempty& ???????? &\circlehalf\\
		\hline 
		GoodUSB\cite{tian2015defending}& \circlefull & \circlefull & \circlefull & \circlefull &\circlefull& \circleempty& \circlefull &\circleempty\\
		\hline

		Neuner et al.\cite{neuner2018usblock}& \circleempty & \circlefull & \circleempty & \circleempty &\circleempty& \circleempty& \circleempty &\circleempty\\
		\hline 
		Pham et al. \cite{pham2010optimizing}& \circleempty & \circleempty & \circleempty & \circlefull &\circlefull& \circleempty& \circleempty &\circleempty\\
		\hline
		JFCGuard\cite{JFC}& \circleempty & \circleempty & \circlefull & \circleempty &\circleempty& \circleempty& \circleempty & ??? \\
			\hline
	\end{tabular}
	\linebreak
    \begin{tablenotes}
	\footnotesize
	\item[1] \circlefull means that the defense is effective
	\item[2] \circlehalf means that the defense is partial effective
	\item[3] \circleempty means that the defense is uneffective
	\end{tablenotes}
	\caption{Effectiveness of defense against different attacks}
	\label{table:attack_vs_defense}
\end{table*}

>>>>

Under the premise of ensuring the full functionality of USB devices, there have been some works trying to improve the security during connection establishment.
Windows Defender ATP\cite{windenfenderwhite} maintains a whitelist of USB devices, only devices on the whitelist are allowed to communicate with the host. This prevents all potential attacks from untrusted devices. But this requires users to have a certain safety awareness and technical background to maintain a valid whitelist. For example, a naive user may add the USB device from unknown sources to his/her whitelist without precaution. There are designs can overcome this drawback. For instance, Mohammadmoradi et al.\cite{mohammadmoradi2018making} proposes a strategy to generate such a whitelist automatically. This strategy first generates a unique fingerprint for each device based on its functionality. Then these fingerprints are used to maintain a safe and valid whitelist of USB devices. There is another work mediating USB connectivity for Industrial Control. TMSUI\cite{yang2015tmsui} relies on rich experience of administrators to build a whitelist. However, some modified USB devices may hide their real functionality from the user.

@@

We summarize the former effort in USB attack and defense in Table~\ref{table:attack_vs_defense}, which illustrates the effectiveness of each defense against various attacks including our \tool.
\newcommand{\circlefull}{\includegraphics[scale=0.025]{Figs/circle_full.png}}
\newcommand{\circlehalf}{\includegraphics[scale=0.025]{Figs/circle_half.png}}
\newcommand{\circleempty}{\includegraphics[scale=0.025]{Figs/circle_empty.png}}
\begin{table*}
	\centering
	\begin{tabular}{|c|c|c|c|c|c|c|c|}

		\hline
		\diagbox[width=1.52in] {Defence}{Attack} & \makecell*[c]{Facedancer\cite{facedancer},\\ Syzkaller\cite{syzkaller}} & \cite{rubber, badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver} & JFC\cite{JFC}&Duqu\cite{duqu},\cite{brain, stuxnet, conficker,flame}&\cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver, usbee, turnip}&\cite{usbkiller, cable}& \tool \\
		\hline
		\makecell{USB condom \cite{Condom}} & \makecell*[c]{\circlefull} & \circlefull & \circlefull &\circlefull& \circlefull&  \circleempty&\circlefull\\
		\hline
		\makecell{
			Windows Defender ATP\cite{windenfenderwhite}, \\
			Mohammadmoradi et al.\cite{mohammadmoradi2018making}, \\
			TMSUI\cite{yang2015tmsui}
		}& \circleempty & \circlehalf & \circlehalf &\circlehalf& \circleempty&  \circleempty &\circlehalf\\

		\hline
		\makecell{GoodUSB\cite{tian2015defending}} & \makecell*[c]{\circlehalf} & \circlefull & \circlefull &\circlefull& \circleempty&  \circleempty &\circleempty\\
		\hline

		\makecell{Neuner et al.\cite{neuner2018usblock}} & \makecell*[c]{\circleempty} & \circlefull & \circleempty &\circleempty& \circleempty& \circleempty &\circleempty\\
		\hline
		\makecell{Pham et al. \cite{pham2010optimizing}} & \makecell*[c]{\circleempty} & \circleempty & \circleempty &\circlefull& \circleempty& \circleempty &\circleempty\\
		\hline
		\makecell{JFCGuard\cite{JFC}} & \makecell*[c]{\circleempty} & \circleempty & \circlefull &\circleempty&  \circleempty  & \circleempty& \circlefull \\
			\hline
	\end{tabular}
	\linebreak
    \begin{tablenotes}
	\footnotesize
	\item[1] \circlefull  \@ means that the defense is effective
	\item[2] \circlehalf \@ means that the defense is partial effective
	\item[3] \circleempty \@  means that the defense is uneffective
	\end{tablenotes}
	\caption{Effectiveness of defense against different attacks}
	\label{table:attack_vs_defense}
\end{table*}
